---
title: "Day_2_Comp_1"
---

## Derivatives in R

Console can be used to install packages, if you want to see if a function will run, using R as a calculator, anything you don't want the history of something.

Everything we need to do this already exists within the R package.

We will use the capital d function (D).

First, we will make an expression for the derivative. Derivative needs the expression (contains our function) inputted with respect to the variable.

```{r}
fx <- expression(3.1 * (x^4) - 28 * x)

#Now storing derivative expression.

df_dx <- D(fx, 'x')

#This will call it back. 
df_dx

x <- 10

#eval evaluating the derivative at the x value that we gave it. 

eval(df_dx)
```

Try finding the slope of g(z) = 2z^3^ -10.5z\^2 + 4.1 at z= 3.6

```{r}
#making the expression. 
gz <- expression (2*z^3 - 10.5*z^2 +4.1)

#finding the derivative, and the variable to which you want to take the derivative with respect to. 

dg_dz <- D(gz, 'z')


#setting z to 3.6 
z<- seq(from =1, to= 3, length =20)

eval(dg_dz)

#running entire chunk, control shift enter!

#what if we wanted to find the slope of the function over a sequence of values. you can easily vectorize to get a slope of multiple values. 

#rendering 
```

Testing a change in this doc.
